Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

\extraspacing {\bf Set $\bm{H'}$.} Take any horizontal segment $h = [x_1, x_2] \times y \in H$. Let $p$ be the rightmost point $p$ on $h$ satisfying the condition that at least one rectangle in $R_{k-2}$ covers $p$. This point $p$ exists if and only if $h$ has at least one left-end covering rectangle in $R_{k-2}$. If $p$ exists and has coordinates $(x, y)$, we refer to the segment $h' = [x_1, x] \times y$ as the {\em trimmed segment} of $h$; conversely, we call $h$ the {\em full segment} of $h'$.

@@

Now, solve a $(k-1)$-SJ problem with $R_1, ..., R_{k-3}, H', V$ as the input using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). Let $\J(R_1, ...,$ $R_{k-3}, H', V)$ represent the result of this $(k-1)$-SJ, whose input size is at most $n$. Given the lemma below (which is proved in Appendix~\ref{app:hv}), we assert that $\J(R_1, ..., R_{k-3}, H', V)$ can be computed in $F_{k-1}(n, \out)$ time.

@@

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Observe that $B_\bm{t}$ --- defined in \eqref{eqn:B_t} --- is a point (due to $h'$ and $v$). Suppose $h' = [x_1, x_2] \times y$ and $B_\bm{t} = (x, y)$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment $[x_1, x] \times y$.

Define
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r \in R_{k-2} \mid \text{ the effective horizontal } \nn \\[-1mm]
    && \text{segment of $\bm{t}$ is contained in $r$}   \}
    \label{eqn:type2:contained-t}
}
The above should not be confused with \eqref{eqn:contained}, where the ``$\contained$'' function takes a segment as the input, rather than a tuple.

@@

        \item Consider any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in \J_2$. Let $h'$ be the trimmed segment of $h$, and set $\bm{t} = (r_1, ..., r_{k-3}, h', v)$. Then, $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$ and $h' \in \contained_{R_{k-2}}(\bm{t})$.

@@

The correctness of the algorithm follows from statements (1) and (2) of Lemma~\ref{lmm:hv:type2:properties}. Furthermore, if we are given $\contained_{R_{k-2}}(\bm{t})$ for each $\bm{t}$, statement (3) of assures us that the algorithm runs in $O(1 + |\J(R_1, ..., R_{k-3}, H', V)| + k \sum_\bm{t} |\contained_{R_{k-2}}(\bm{t})|) = O(1 + k \cdot \out)$ time, where the derivation used Lemma~\ref{lmm:hv:type2:recur-output} and statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

>>>>

\extraspacing {\bf Set $\bm{H'}$.} Take any horizontal segment $h = [x_1, x_2] \times y \in H$. Let $p$ be the rightmost point on $h$ satisfying the condition that at least one rectangle in $R_{k-2}$ covers $p$. This $p$ exists if and only if $h$ has at least one left-end covering rectangle in $R_{k-2}$. If $p$ exists and has coordinates $(x, y)$, we refer to the segment $h' = [x_1, x] \times y$ as the {\em trimmed segment} of $h$; conversely, we call $h$ the {\em full segment} of $h'$.

@@

Now, solve a $(k-1)$-SJ problem on the input $\set{R_1, ..., R_{k-3}, H', V}$ using the algorithm $\A$ supplied (by Lemma~\ref{lmm:hv}). Let $\J(R_1, ...,$ $R_{k-3}, H', V)$ represent the result of this $(k-1)$-SJ, whose input size is at most $n$. Given the lemma below (which is proved in Appendix~\ref{app:hv}), we assert that $\J(R_1, ..., R_{k-3}, H', V)$ can be computed in $F_{k-1}(n, \out)$ time.

@@

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $B_\bm{t}$ --- defined in \eqref{eqn:B_t} --- is a point (due to $h'$ and $v$). Suppose $h' = [x_1, x_2] \times y$ and $B_\bm{t} = (x, y)$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment $[x_1, x] \times y$. This allows us to define
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r \in R_{k-2} \mid \text{ the effective horizontal } \nn \\[-1mm]
    && \text{segment of $\bm{t}$ is contained in $r$}   \}
    \label{eqn:type2:contained-t}
}
The above should not be confused with \eqref{eqn:contained}, where the ``$\contained$'' function takes a segment as the parameter, rather than a tuple.

@@

        \item Consider any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in \J_2$. Let $h'$ be the trimmed segment of $h$ and set $\bm{t} = (r_1, ..., r_{k-3}, h', v)$. Then, $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$ and $h' \in \contained_{R_{k-2}}(\bm{t})$.

@@

The correctness of the algorithm follows from statements (1) and (2) of Lemma~\ref{lmm:hv:type2:properties}. Furthermore, if we are given $\contained_{R_{k-2}}(\bm{t})$ for each $\bm{t}$, statement (3) of Lemma~\ref{lmm:hv:type2:properties}
assures us that the algorithm runs in $O(1 + |\J(R_1, ..., R_{k-3}, H', V)| + k \sum_\bm{t} |\contained_{R_{k-2}}(\bm{t})|) = O(1 + k \cdot \out)$ time, where the derivation used Lemma~\ref{lmm:hv:type2:recur-output} and statement (3) of Lemma~\ref{lmm:hv:type2:properties}.
